Family Fortunes: A Quantitative Analysis of the Early Iron Age Cemeteries at Knossos, Crete

### 2019-03-29 analysis/paper/paper.Rmd
gini estimates

library(reshape)
library(data.table)
library(extrafont)
library(ggplot2)
library(RColorBrewer)
library(grid)
library(dplyr)
font_import(paths="../paper/font",pattern="GARA")
loadfonts(device="win")

@@

>>>>

library(ineq)
library(ggrepel)
library(reshape)
library(data.table)
library(extrafont)
library(ggplot2)
library(RColorBrewer)
library(grid)
library(dplyr)
font_import(paths="../paper/font",pattern="GARA")
loadfonts(device="win")

@@

                   #geom_label_repel(data=subset(aorist_melt,aorist_melt$value>8 & aorist_melt$variable=="710"),
                      #aes(label=tomb), show.legend = FALSE,ylim=c(0,40))

tombs_gini<-matrix(0, ncol = 0, nrow = 1)
tombs_gini<-data.frame(tombs_gini)
for(i in colnames(aorist_tomb_values[2:51])) {
  tombs_gini[[paste0(i)]] <- ineq(aorist_tomb_vals_only[[i]],type="Gini")
}

View(tombs_gini)

tombs_gini<-t(tombs_gini)
tombs_gini<-data.frame(tombs_gini)

colnames(tombs_gini)<-c("gini_coefficient")
row.names(tombs_gini)<-dates
tombs_gini<-data.frame(tombs_gini)
setDT(tombs_gini, keep.rownames = "decade")
tombs_gini$decade<-as.numeric(tombs_gini$decade)

ggplot(tombs_gini,aes(decade,gini_coefficient))+geom_line()+
      xlim(1100,600)+ylim(0.3,0.8)+theme_minimal()+
        theme(legend.title=element_blank(),
          text=element_text(family="Garamond", size=12))+
              labs(x="Date (Years BC)", y="Gini Coefficient")+
                 scale_fill_brewer(palette = "Set2")

rects <- data.frame(xstart = c(1100,970,920,875,840,810,790,745,70,670,630), 
                    xend = c(970,920,875,840,810,790,745,710,670,630,600), 
                    col = c("SM", "EPG", "MPG", "LPG", "PGB", "EG", "MG", "LG", "EO", "LO","A"))
rects$col<-factor(rects$col,levels=c("SM", "EPG", "MPG", "LPG", "PGB", "EG", "MG", "LG", "EO", "LO","A"))

ggplot() + 
  geom_rect(data = rects, aes(xmin = xstart, xmax = xend, ymin = -Inf, ymax = Inf, fill = col), alpha = 0.4) +
     geom_line(data = tombs_gini, aes(decade,gini_coefficient))+xlim(1100,600)+ylim(0.5,0.8)+
      theme_bw()+theme(legend.title=element_blank(),
          text=element_text(family="Garamond", size=12))+
              labs(x="Date (Years BC)", y="Gini Coefficient")+
                 scale_fill_brewer(palette = "Set3")+ scale_x_reverse(expand = c(0, 0),limits=c(1100,600))+
                    scale_y_continuous(expand = c(0, 0),limits=c(0.5,0.8))

plot(Lc(aorist_tomb_values$`800`))
